---
title: "rGlobi- CALeDNA 1 dataset any taxononmic level"
output: html_document
---
load/Install required Libraries
```{r}
library(rglobi)
library(tidyverse)
library(dplyr)
library(igraph)
library(networkD3)
library(visNetwork)
```

Provide a path to the a CALeDNA taxonomy ASV sum by taxonomy table in .txt format.
You can download some example data from the LA_river project here: https://data.ucedna.com/research_projects/los-angeles-river/pages/appendix
```{r}
taxonomytable<-read.delim("/Users/samuelrapp/RStudio/MeyersLab/eDNA_rGlobi/LA_river_data/LA_river_X12S_ASV_sum_by_taxonomy_70_dc_ed_min5_LA_river_X12S_ASV_sum_by_taxonomy_70_dc_ed_min5.txt")
taxonomy_only_table <-select(taxonomytable, sum.taxonomy) %>% 
  separate(sum.taxonomy, c("domain", "phylum", "class", "order", "family", "genus", "genus_species"), sep = ";",remove=FALSE)
```

The previous block divided the sum.taxonomy column into seperate columns.
Pick any one taxonomic rank of interest(ie. a column), and remove all NA/"" empty values from that column. 
```{r}
taxonomic_rank_of_interest <- "family" #Put in Qoutes the taxonomic rank: "genus","family", etc you want rGlobi to explore!
taxonomic_rank_column_number <- which(colnames(taxonomy_only_table) == taxonomic_rank_of_interest)
#values used later for naming columns/rows in matrix

#Fill in by text (NOT using the variable taxonomic_rank_of_interest) the taxonomic rank of interest following the dollar signs '$'
#this line filters out NA/"" empty cells 
taxonomy_only_table<-taxonomy_only_table[!(taxonomy_only_table$family == "" | taxonomy_only_table$family=="NA"), ]

#remove duplicate rows #write in taxonomic rank of interest as first variable in distinct(write here,)
taxonomy_only_table<- taxonomy_only_table %>% distinct(family, .keep_all = TRUE)
```

Creates matrixes who's columns and rows match the column previously picked ("family", "genus", "etc"):
Both matrixes have the same rows and columns, but how they will be populated differentiates them.
```{r}
number_eDNA_spp <- nrow(taxonomy_only_table)

#matrix to hold true false values
BinaryMatrix <- matrix(NA, number_eDNA_spp, number_eDNA_spp)
#add species names to the columns/rows 
colnames(BinaryMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,taxonomic_rank_column_number]
rownames(BinaryMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,taxonomic_rank_column_number]
#matrix to hold interaction value 
InteractionMatrix <- matrix(NA, number_eDNA_spp,number_eDNA_spp)

colnames(InteractionMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,taxonomic_rank_column_number]
rownames(InteractionMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,taxonomic_rank_column_number]
```

Function returns true(1) or false(0), when given the output of the rGlobi function get_interactions_by_taxa(, , showfield = c("source_taxon_name", "interaction_type", "target_taxon_name")). This function's output populates the BinaryMatrix.
```{r}
do_they_interact <-  function(rGlobiResult)
{
  NUMBER_OF_INTERACTIONS <- nrow(rGlobiResult)
  if(NUMBER_OF_INTERACTIONS<1)
  {
    OUTPUT <- FALSE
  }
  else {
    OUTPUT <- TRUE
    
  }
  return(OUTPUT)
}
```

Function returns the a text string of rGlobi interaction by concatenating dataframe cells that holds the first interaction type result from a rGlobi get_interactions_by_taxa. Note: There may be more than 1 interaction between X and Y but we are only reporting the first Globi result. This function's output populates the InteractionMatrix.
```{r}
how_they_interact <-  function(rGlobiResult)
{
    INTERACTION <- rGlobiResult[1,2] 
    #should be the proper cell/index in the dataframe, if this formatting is used
    #get_interactions_by_taxa(taxa1,taxa2, showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=1)) 
    Species <- rGlobiResult[1,1]
    Species2<- rGlobiResult[1,3]
    INTERACTION<-paste0(Species," ", INTERACTION, " ", Species2)
    return(INTERACTION)
}
```

Nested for loops populate the BinaryMatrix and InteractionMatrix.
The BinaryMatrix is filled with 1s, which mean Globi found a relationship, and 0s, Globi didn't find a relationship. 
The InteractionMatrix is filled with a text value like... "species x 'preys on' spexies y", and is NA otherwise.
```{r}
for(i in 1:number_eDNA_spp)
{
  source_species <- taxonomy_only_table[i,taxonomic_rank_column_number]
    
  for(j in i:number_eDNA_spp)
  {
  
    target_species<-taxonomy_only_table[j,taxonomic_rank_column_number]
      
 interaction_result <-get_interactions_by_taxa(source_species, target_species, showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=1)) 

    if(TRUE==do_they_interact(interaction_result))
    {
      BinaryMatrix[i,j]<-1#true
      InteractionMatrix[i,j]<-how_they_interact(interaction_result)
      # print(how_they_interact(interaction_result))
    }
    else
    {
       BinaryMatrix[i,j]<-0#FALSE
       InteractionMatrix[i,j]<-"NA"
    }
  }
}

print("Matrix population COMPLETE")

```

Function: sum of interactions: Takes Populated BinaryMatrix and sums the number of interactions for each species.
```{r}
sum_interactions_1group <-function(BinaryMatrix, summary_stats)
{
  number_of_species <- nrow(BinaryMatrix)
  
  sum_interactions_column_number <- which(colnames(summary_stats) == "sum_interactions")
  
  BMcolsums <-colSums(BinaryMatrix, na.rm= TRUE) 
  BMrowsums <- rowSums(BinaryMatrix, na.rm = TRUE)

  for(i in 1:number_of_species)
  {
    if(BinaryMatrix[i,i] == 1)    
    {
      summary_stats[i,sum_interactions_column_number] <- BMcolsums[[i]] + BMrowsums[[i]] - 1
    }
    else
    {
      summary_stats[[i,sum_interactions_column_number]] <- BMcolsums[[i]] + BMrowsums[[i]]
    }
     print(BMcolsums[[i]] + BMrowsums[[i]])
  }
  return(summary_stats) 
}
```

Summary Stats: Generate new table from BinaryMatrix. So far we only have 1 summary stat: sum of interactions...
```{r}
summary_stats<-matrix(NA, number_eDNA_spp, 3) #last field depends on how many variables we want to work with. The number, 3 in this case, must match the following two lines.
summary_stats_columns <- c("sum_interactions", "will add more functions later", "extra column") #3 strings
colnames(summary_stats)[1:3] <- summary_stats_columns #adding those 3 strings
summary_stats <- sum_interactions_1group(BinaryMatrix, summary_stats)
rownames(summary_stats)[1:number_eDNA_spp] <- taxonomy_only_table[,taxonomic_rank_column_number]
view(summary_stats)

#other potential options
#number of interactions between groups
#interaction rate amoung/between groups...
```

Creating Graph Networks from BinaryMatrix, using iGraph package.
```{r}
network <- graph_from_adjacency_matrix(BinaryMatrix, mode='undirected', diag =F, weighted=TRUE)
edge.list<-get.edgelist(network) #https://stackoverflow.com/questions/24742882/r-igraph-convert-a-weighted-adjacency-matrix-into-weighted-edgelist
# edge.list2<-get.edgelist(BinaryMatrix)
#https://www.r-graph-gallery.com/248-igraph-plotting-parameters.html
network2 <- graph_from_adjacency_matrix(BinaryMatrix, mode='undirected', diag =F)

 # graph_from_adjacency_matrix?
deg <- degree(network, mode="all") # Count the number of degree for each node:
# plot(network, vertex.label.cex = .75, vertex.size= deg*3,  vertex.label.color=c("black"), layout=layout.fruchterman.reingold, main="fruchterman.reingold")
# datafrane1<-as.data.frame(BinaryMatrix)
# visNetwork(datafrane1)
# simpleNetwork(datafrane1)
# class(BinaryMatrix)
# simpleNetwork(datafrane1)
plot(network, vertex.shape="none", layout=layout.random, vertex.label.cex = deg*.25, vertex.label.color=c("black"), main="random")

plot(network, vertex.shape="none", layout= layout.circle, vertex.label.cex = deg*.25, vertex.label.color=c("black"))

plot(network, vertex.shape="none", layout=layout.circle, vertex.label.cex = deg*.25, vertex.label.color=c("black"))


plot(network, layout=layout.sphere, vertex.size= deg*3, main="sphere")
plot(network, layout=layout.circle, vertex.size= deg*3, main="circle")
plot(network, layout=layout.random, vertex.size= deg*3, main="random")
plot(network, layout=layout.random, vertex.size= deg*3) #, main="random")
plot(network, layout=layout.fruchterman.reingold, vertex.size= deg*3, main="fruchterman.reingold")

```

































