---
title: "rGlobi- CALeDNA data"
output: html_document
---
Install Library rglobi
```{r}
library(rglobi)
library(tidyverse)
library(dplyr)
```

import taxnomy data file and create lists for- eDNA file (we will only work we eDNA results in v1) then add iNat File
```{r}
taxonomytable<-read.delim("/Users/samuelrapp/RStudio/MeyersLab/eDNA_rGlobi/LA_river_data/LA_river_X12S_ASV_sum_by_taxonomy_70_dc_ed_min5_LA_river_X12S_ASV_sum_by_taxonomy_70_dc_ed_min5.txt")
taxonomy_only_table <-select(taxonomytable, sum.taxonomy) %>% 
  separate(sum.taxonomy, c("domain", "phylum", "class", "order", "family", "genus", "genus species"), sep = ";",remove=FALSE)
  #change taxon data to only have genus_spp, what rGlobi accepts as an argument
```

fill in "" empty values in taxonomy table
```{r}
genus_species_column_number <- which(colnames(taxonomy_only_table) == "genus species")
genus_column_number <- which(colnames(taxonomy_only_table) == "genus")
#values used later for naming columns/rows in matrix

number_eDNA_spp <-nrow(taxonomy_only_table)

for(i in 1:number_eDNA_spp)
  {
    if(taxonomy_only_table[i,genus_species_column_number] == "" || taxonomy_only_table[i,genus_species_column_number] == "NA")
    {
      taxonomy_only_table[i,genus_species_column_number] = "Missing Spp-genus"
    }
    if(taxonomy_only_table[i,genus_column_number] == "" || taxonomy_only_table[i, genus_column_number] == "NA")
    {
      taxonomy_only_table[i,genus_column_number] = "Missing Genus"
    }
}

```


(this step can be skipped in V1)
compare two lists and create 3rd list of species shared in eDNA and iNat results 
Spit out some summary stats of that 
```{r}
#list vs list -> new list
```


create dataframe/matrixs that match the length of the lists:
```{r}
#matrix to hold true false values
BinaryMatrix <- matrix(NA, number_eDNA_spp, number_eDNA_spp)
#add species names to the columns/rows 
colnames(BinaryMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,genus_species_column_number]
rownames(BinaryMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,genus_species_column_number]
#matrix to hold interaction value 
InteractionMatrix <- matrix(NA, number_eDNA_spp,number_eDNA_spp)

colnames(InteractionMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,genus_species_column_number]
rownames(InteractionMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,genus_species_column_number]
```


Function outputs true or false, when given the output of the rGlobi function get_interactions_by_taxa(, , showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"))
```{r}
do_they_interact <-  function(rGlobiResult)
{
  NUMBER_OF_INTERACTIONS <- nrow(rGlobiResult)
  if(NUMBER_OF_INTERACTIONS<1)
  {
    OUTPUT <- FALSE
  }
  else {
    OUTPUT <- TRUE
    
  }
  return(OUTPUT)
}
```

function returns the dataframe cell that holds the first interaction type result from a rGlobi get_interactions_by_taxa. It will return NA if the species don't interact
```{r}
how_they_interact <-  function(rGlobiResult)
{
    INTERACTION <- rGlobiResult[1,2] 
    #should be the proper cell/index in the dataframe, if this formatting is used
    #get_interactions_by_taxa(taxa1,taxa2, showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=1)) 
    Species <- rGlobiResult[1,1]
    Species2<- rGlobiResult[1,3]
    test<-paste0(Species," ", INTERACTION, " ", Species2)
    return(test)
    # return(INTERACTION)
}
```


take list and run it through a nested for loop to populate a matrix...
```{r}
for(i in 1:number_eDNA_spp)
{
  if("Missing Spp-genus" == (taxonomy_only_table[i,genus_species_column_number])) #no genus-species value
    {
      source_species <- taxonomy_only_table[i,genus_column_number]
     print(paste0("I no spp ","row:",i," column: ",genus_species_column_number, source_species))
      
    }
       else
       {
        source_species <- taxonomy_only_table[i,genus_species_column_number]
       print(paste0("I yes spp ","row:",i," column:",genus_species_column_number))
       }
  
  for(j in i:number_eDNA_spp)
  {
    if("Missing Spp-genus" == (taxonomy_only_table[j,genus_species_column_number]))
    {
      target_species <- taxonomy_only_table[j,genus_column_number]
     print(paste0("J no spp ","row:",j," column:",genus_species_column_number, target_species))
    }
    else
    {
      target_species<-taxonomy_only_table[j,genus_species_column_number]
       print(paste0("J yes spp ","row:",j," column: ",genus_species_column_number))
    }

  interaction_result <-get_interactions_by_taxa(source_species, target_species, showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=1)) 

    if(TRUE==do_they_interact(interaction_result))
    {
      BinaryMatrix[i,j]<-1#true
      InteractionMatrix[i,j]<-how_they_interact(interaction_result)
      print(how_they_interact(interaction_result))
    }
    else
    {
       BinaryMatrix[i,j]<-0#FALSE
       InteractionMatrix[i,j]<-"NA"
       # print("NA")
    }
  }
}


```

sum of interactions: for results coming from comparing 1 set of species against itself
```{r}
sum_interactions_1group <-function(BinaryMatrix, summary_stats)
{
  number_of_species <- nrow(BinaryMatrix)
  
  sum_interactions_column_number <- which(colnames(summary_stats) == "sum_interactions")
  
  BMcolsums <-colSums(BinaryMatrix, na.rm= TRUE) 
  BMrowsums <- rowSums(BinaryMatrix, na.rm = TRUE)

  # summary_stats[1,sum_interactions_column_number] <- BMcolsums[[1]] + BMrowsums[[1]]
  # summary_stats[1,sum_interactions_column_number]
  for(i in 1:number_of_species)
  {
    if(BinaryMatrix[i,i] == 1)    
    {
      summary_stats[i,sum_interactions_column_number] <- BMcolsums[[i]] + BMrowsums[[i]] - 1
      print("hi-1")
    }
    else
    {
      summary_stats[[i,sum_interactions_column_number]] <- BMcolsums[[i]] + BMrowsums[[i]]
      print("hi")
    }
     print(BMcolsums[[i]] + BMrowsums[[i]])
  }
  return(summary_stats) 
}

```


print out T/F matrix and print out 1st interaction matrix
```{r}
#print()
summary_stats<-matrix(NA, number_eDNA_spp, 3) #depends on how many variables we want to work with,
summary_stats_columns <- c("sum_interactions", "will add more functions later", "extra column")
colnames(summary_stats)[1:3] <- summary_stats_columns
#sum will be a good starting place
summary_stats <- sum_interactions_1group(BinaryMatrix, summary_stats)
#function find total number of interactions a species has...
 
rownames(summary_stats)[1:number_eDNA_spp] <- taxonomy_only_table[,genus_species_column_number]
#print()
```

print out global counts
```{r}
#number of interactions between groups
#interaction rate amoung/between groups...
#species with greatest number of interactions... (could write a function that reads a t/f matrix easily)
```


































