---
title: "rGlobi- CALeDNA data"
output: html_document
---
Install Library rglobi
```{r}
library(rglobi)
library(tidyverse)
library(dplyr)
```

import taxnomy data file and create lists for- eDNA file (we will only work we eDNA results in v1) then add iNat File
```{r}
taxonomytable<-read.delim("/Users/samuelrapp/RStudio/MeyersLab/eDNA_rGlobi/LA_river_taxnomy_table.txt")
taxonomy_only_table <-select(taxonomytable, sum.taxonomy) %>% 
  separate(sum.taxonomy, c("domain", "phylum", "class", "order", "family", "genus", "genus species"), sep = ";",remove=FALSE)
  #change taxon data to only have genus_spp, what rGlobi accepts as an argument

genus_species_column_number <- which(colnames(taxonomy_only_table)=="genus species")
genus_column_number <- which(colnames(taxonomy_only_table)=="genus")
#values used later for naming columns/rows in matrix

number_eDNA_spp <-nrow(taxonomy_only_table)
```

(this step can be skipped in V1)
compare two lists and create 3rd list of species shared in eDNA and iNat results 
Spit out some summary stats of that 
```{r}
#list vs list -> new list
```


create dataframe/matrixs that match the length of the lists:
```{r}
#matrix to hold true false values
BinaryMatrix <- matrix(NA, number_eDNA_spp, number_eDNA_spp)
#add species names to the columns/rows 
colnames(BinaryMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,genus_species_column_number]
rownames(BinaryMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,genus_species_column_number]
#matrix to hold interaction value 
InteractionMatrix <- matrix(NA, number_eDNA_spp,number_eDNA_spp)

colnames(InteractionMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,genus_species_column_number]
rownames(InteractionMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,genus_species_column_number]
```


Function outputs true or false, when given the output of the rGlobi function get_interactions_by_taxa(, , showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"))
```{r}
do_they_interact <-  function(rGlobiResult)
{
  NUMBER_OF_INTERACTIONS <- nrow(rGlobiResult)
  if(NUMBER_OF_INTERACTIONS<1)
  {
    OUTPUT <- FALSE
  }
  else {
    OUTPUT <- TRUE
    
  }
  return(OUTPUT)
}
```

function returns the dataframe cell that holds the first interaction type result from a rGlobi get_interactions_by_taxa. It will return NA if the species don't interact
```{r}
how_they_interact <-  function(rGlobiResult)
{
    INTERACTION <- rGlobiResult[1,2] 
    #should be the proper cell/index in the dataframe, if this formatting is used
    #get_interactions_by_taxa(taxa1,taxa2, showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=1)) 
    Species <- rGlobiResult[1,1]
    Species2<- rGlobiResult[1,3]
    test<-paste0(INTERACTION, Species, Species2)
    return(test)
    # return(INTERACTION)
}
```


take list and run it through a nested for loop to populate a matrix...
```{r}
for(i in 1:number_eDNA_spp)
{
  if(""==(taxonomy_only_table[i,genus_species_column_number])) #no genus-species value
    {
      source_species <- taxonomy_only_table[i,genus_column_number]
      print(paste0("I no spp ","row:",i," column:",genus_species_column_number, source_species))
      
    }
       else
       {
        source_species <- taxonomy_only_table[i,genus_species_column_number]
        print(paste0("I yes spp ","row:",i," column:",genus_species_column_number))
       }
  
  for(j in i:5)
  {
    if(""==(taxonomy_only_table[j,genus_species_column_number]))
    {
      target_species <- taxonomy_only_table[j,genus_column_number]
      print(paste0("J no spp ","row:",j," column:",genus_species_column_number, target_species))
    }
    else
    {
      target_species<-taxonomy_only_table[j,genus_species_column_number]
       print(paste0("J yes spp ","row:",j," column:",genus_species_column_number))
    }
   
  
   # p1<-is.null(taxonomy_only_table[1,3])
   #  p1<-is.null(taxonomy_only_table[1,3])
   #     print(p1)  
   #     print( taxonomy_only_table[1,3] )
   #     taxonomy_only_table[1,3] == ""
     #create genus_spp string by combining(or pasting results) from the taxonomy columns
 ## source_species <- paste(taxonomy_only_table[i,genus_column_number], taxonomy_only_table[i,genus_species_column_number], sep=" ")
  ##target_species <-paste(taxonomy_only_table[j,genus_column_number], taxonomy_only_table[j,genus_species_column_number],sep=" ")

  interaction_result <-get_interactions_by_taxa(source_species, target_species, showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=1)) 
  # v1<-""
  # v2<-""
  #  interaction_result2 <-get_interactions_by_taxa(v2,v1, showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=10))
  #  interaction_result2
  #be careful about the limit, you have to make sure were only comparing  species to another at a time. If we are comparing lists and we write limit we   may loss results
  x<-get_interactions_by_taxa("V3", "X", showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=1)) 
  x
  if(TRUE==do_they_interact(interaction_result))
  {
    BinaryMatrix[i,j]<-1#true
    InteractionMatrix[i,j]<-how_they_interact(interaction_result)
    print(how_they_interact(interaction_result))
     print(paste0("source species:", source_species))
     print(paste0("target species:", target_species))
  }
  else
  {
     BinaryMatrix[i,j]<-0#FALSE
     InteractionMatrix[i,j]<-"NA"
     # print("NA")
  }
#BinaryMatrix[i][j]<-do_they_interact(interaction_result)
  #fill T/F matrix[][] =do_they_interact(result)
 # if true
  #fill value matrix[][]=how_they_interact(result)
  #else ##if false
  #fill matrix[][]="NA"
  }
}


```

print out T/F matrix and print out 1st interaction matrix
```{r}
#print()
#print()
```

print out global counts
```{r}
#number of interactions between groups
#interaction rate amoung/between groups...
#species with greatest number of interactions... (could write a function that reads a t/f matrix easily)
```


































