---
title: "rGlobi- CALeDNA data"
output: html_document
---
Install Library rglobi
```{r}
library(rglobi)
library(tidyverse)
```

import taxnomy data file and create lists for- eDNA file (we will only work we eDNA results in v1) then add iNat File
```{r}
taxonomytable<-read.delim("LA_river_taxnomy_table-Sheet1.txt")
rea
#change taxon data to only have genus_spp, what rGlobi accepts as an argument
```

(this step can be skipped in V1)
compare two lists and create 3rd list of species shared in eDNA and iNat results 
Spit out some summary stats of that 
```{r}
#list vs list -> new list
```


create matrixs that match the length of the lists:
```{r}
#matrix to hold true false values
#matrix to hold interaction value 
```

take list and run it through a nested for loop to populate a matrix...
```{r}
for(i in 1:n)
{
  for(j in i:n)
  {
  result<-get_interactions_by_taxa(eDNAlist[[i]],eDNAlist[[j]], showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=1)) 
  #be careful about the limit, you have to make sure were only comparing  species to another at a time. If we are comparing lists and we write limit we may loss results
  #
  #fill T/F matrix[][] =do_they_interact(result)
 # if true
  #fill value matrix[][]=how_they_interact(result)
  #else ##if false
  #fill matrix[][]="NA"
  }
}


```


Function outputs true or false, when given the output of the rGlobi function get_interactions_by_taxa(, , showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"))
```{r}
do_they_interact <-  function(rGlobiResult)
{
  NUMBER_OF_INTERACTIONS <- nrow(rGlobiResult)
  if(NUMBER_OF_INTERACTIONS<1)
  {
    OUTPUT <- FALSE
  }
  else {
    OUTPUT <- TRUE
    
  }
  return(OUTPUT)
}
```

function returns the dataframe cell that holds the first interaction type result from a rGlobi get_interactions_by_taxa. It will return NA if the species don't interact
```{r}
how_they_interact <-  function(rGlobiResult)
{
    INTERACTION <- rGlobiResult[1,2] 
    #should be the proper cell/index in the dataframe, if this formatting is used
    #get_interactions_by_taxa(taxa1,taxa2, showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=1)) 
    return(INTERACTION)
}
```


print out T/F matrix and print out 1st interaction matrix
```{r}
#print()
#print()
```

print out global counts
```{r}
#number of interactions between groups
#interaction rate amoung/between groups...
#species with greatest number of interactions... (could write a function that reads a t/f matrix easily)
```


































