---
title: "rGlobi- CALeDNA 1 dataset any taxononmic level"
output: html_document
---
Install Library rglobi
```{r}
library(rglobi)
library(tidyverse)
library(dplyr)
library(igraph)
```

import taxnomy data file and create lists for- eDNA file (we will only work we eDNA results in v1) then add iNat File
```{r}
taxonomytable<-read.delim("/Users/samuelrapp/RStudio/MeyersLab/eDNA_rGlobi/LA_river_data/LA_river_X12S_ASV_sum_by_taxonomy_70_dc_ed_min5_LA_river_X12S_ASV_sum_by_taxonomy_70_dc_ed_min5.txt")
taxonomy_only_table <-select(taxonomytable, sum.taxonomy) %>% 
  separate(sum.taxonomy, c("domain", "phylum", "class", "order", "family", "genus", "genus_species"), sep = ";",remove=FALSE)
  #change taxon data to only have genus_spp, what rGlobi accepts as an argument
```

pick taxonomic rank of interest, and remove all NA/"" empty values from that column. 
```{r}
taxonomic_rank_of_interest <- "family" #Put in Qoutes the taxonomic rank: "genus","family", etc you want rGlobi to compare with.
taxonomic_rank_column_number <- which(colnames(taxonomy_only_table) == taxonomic_rank_of_interest)
#values used later for naming columns/rows in matrix

#Fill in by text (NOT using the variable taxonomic_rank_of_interest) the taxonomic rank of interest following the dollar signs '$'
#filters out NA/"" empty cells
taxonomy_only_table<-taxonomy_only_table[!(taxonomy_only_table$family == "" | taxonomy_only_table$family=="NA"), ]

#remove duplicate rows #write in taxonomic rank of interest as first variable in distinct(write here,)
taxonomy_only_table<- taxonomy_only_table %>% distinct(family, .keep_all = TRUE)
```


(this step can be skipped in V1)
compare two lists and create 3rd list of species shared in eDNA and iNat results 
Spit out some summary stats of that 
```{r}
#list vs list -> new list
```


create dataframe/matrixs that match the length of the lists:
```{r}
number_eDNA_spp <- nrow(taxonomy_only_table)

#matrix to hold true false values
BinaryMatrix <- matrix(NA, number_eDNA_spp, number_eDNA_spp)
#add species names to the columns/rows 
colnames(BinaryMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,taxonomic_rank_column_number]
rownames(BinaryMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,taxonomic_rank_column_number]
#matrix to hold interaction value 
InteractionMatrix <- matrix(NA, number_eDNA_spp,number_eDNA_spp)

colnames(InteractionMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,taxonomic_rank_column_number]
rownames(InteractionMatrix)[1:number_eDNA_spp]<-taxonomy_only_table[,taxonomic_rank_column_number]
```


Function outputs true or false, when given the output of the rGlobi function get_interactions_by_taxa(, , showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"))
```{r}
do_they_interact <-  function(rGlobiResult)
{
  NUMBER_OF_INTERACTIONS <- nrow(rGlobiResult)
  if(NUMBER_OF_INTERACTIONS<1)
  {
    OUTPUT <- FALSE
  }
  else {
    OUTPUT <- TRUE
    
  }
  return(OUTPUT)
}
```

function returns the dataframe cell that holds the first interaction type result from a rGlobi get_interactions_by_taxa. It will return NA if the species don't interact
```{r}
how_they_interact <-  function(rGlobiResult)
{
    INTERACTION <- rGlobiResult[1,2] 
    #should be the proper cell/index in the dataframe, if this formatting is used
    #get_interactions_by_taxa(taxa1,taxa2, showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=1)) 
    Species <- rGlobiResult[1,1]
    Species2<- rGlobiResult[1,3]
    INTERACTION<-paste0(Species," ", INTERACTION, " ", Species2)
    return(INTERACTION)
}
```


take list and run it through a nested for loop to populate a matrix...
```{r}
for(i in 1:number_eDNA_spp)
{
  source_species <- taxonomy_only_table[i,taxonomic_rank_column_number]
    
  for(j in i:number_eDNA_spp)
  {
  
    target_species<-taxonomy_only_table[j,taxonomic_rank_column_number]
      
 interaction_result <-get_interactions_by_taxa(source_species, target_species, showfield = c("source_taxon_name", "interaction_type", "target_taxon_name"), otherkeys = list("limit"=1)) 

    if(TRUE==do_they_interact(interaction_result))
    {
      BinaryMatrix[i,j]<-1#true
      InteractionMatrix[i,j]<-how_they_interact(interaction_result)
      print(how_they_interact(interaction_result))
    }
    else
    {
       BinaryMatrix[i,j]<-0#FALSE
       InteractionMatrix[i,j]<-"NA"
       # print("NA")
    }
  }
}

print("ANALYSIS COMPLETE")

```

sum of interactions: for results coming from comparing 1 set of species against itself
```{r}
sum_interactions_1group <-function(BinaryMatrix, summary_stats)
{
  number_of_species <- nrow(BinaryMatrix)
  
  sum_interactions_column_number <- which(colnames(summary_stats) == "sum_interactions")
  
  BMcolsums <-colSums(BinaryMatrix, na.rm= TRUE) 
  BMrowsums <- rowSums(BinaryMatrix, na.rm = TRUE)

  for(i in 1:number_of_species)
  {
    if(BinaryMatrix[i,i] == 1)    
    {
      summary_stats[i,sum_interactions_column_number] <- BMcolsums[[i]] + BMrowsums[[i]] - 1
    }
    else
    {
      summary_stats[[i,sum_interactions_column_number]] <- BMcolsums[[i]] + BMrowsums[[i]]
    }
     print(BMcolsums[[i]] + BMrowsums[[i]])
  }
  return(summary_stats) 
}

```


print out T/F matrix and print out 1st interaction matrix
```{r}
#print()
summary_stats<-matrix(NA, number_eDNA_spp, 3) #depends on how many variables we want to work with,
summary_stats_columns <- c("sum_interactions", "will add more functions later", "extra column")
colnames(summary_stats)[1:3] <- summary_stats_columns
#sum will be a good starting place
summary_stats <- sum_interactions_1group(BinaryMatrix, summary_stats)
#function find total number of interactions a species has...
rownames(summary_stats)[1:number_eDNA_spp] <- taxonomy_only_table[,taxonomic_rank_column_number]
view(summary_stats)
#print()
```

print out global counts
```{r}
#number of interactions between groups
#interaction rate amoung/between groups...
#species with greatest number of interactions... (could write a function that reads a t/f matrix easily)
```

print out graphnetwork:
```{r}
network <- graph_from_adjacency_matrix(BinaryMatrix, mode='undirected', diag =F)
#https://www.r-graph-gallery.com/248-igraph-plotting-parameters.html

 
deg <- degree(network, mode="all") # Count the number of degree for each node:
plot(network, vertex.label.cex = .75, vertex.size= deg*3,  vertex.label.color=c("black"), layout=layout.fruchterman.reingold, main="fruchterman.reingold")


plot(network, layout=layout.random, vertex.size= deg*3, main="random")
plot(network, layout=layout.sphere, vertex.size= deg*3, main="sphere")
plot(network, layout=layout.circle, vertex.size= deg*3, main="circle")
plot(network, layout=layout.random, vertex.size= deg*3, main="random")
plot(network, layout=layout.fruchterman.reingold, vertex.size= deg*3, main="fruchterman.reingold")

```

































